Models of lens candidates from Space Warps CFHTLS

### 2016-11-23 paper2.tex
figure changes

\def\includeten#1#2{
\includegraphics[width=\pwidth]{#1ASW0007k4r_N7LTELSYTM#2}%
\includegraphics[width=\pwidth]{#1ASW00096rm_4Q3YCEWGLN#2}%
\includegraphics[width=\pwidth]{#1ASW0007xrs_JHC3J2HYV7#2}\\
\includegraphics[width=\pwidth]{#1ASW0007iwp_4XBJWT3COV#2}%
\includegraphics[width=\pwidth]{#1ASW000619d_011489#2}%
\includegraphics[width=\pwidth]{#1ASW0001ld7_OS3CYAKLRT#2}\\
\includegraphics[width=\pwidth]{#1ASW0002asp_5EKMWWVJHL#2}%
%\includegraphics[width=\pwidth]{#1ASW000096t_7IPP7LWVOF#2}%
\includegraphics[width=\pwidth]{#1ASW0008qsm_TOFS7JNGEK#2}%
\includegraphics[width=\pwidth]{#1ASW0008pag_5SXGXQYY6V#2}\\
}

\def\includezehn#1#2{
\includegraphics[width=\pwidth]{#1SW05_ASW0007k4r_N7LTELSYTM#2}%
\includegraphics[width=\pwidth]{#1SW42_ASW00096rm_4Q3YCEWGLN#2}%
\includegraphics[width=\pwidth]{#1SW28_ASW0007xrs_JHC3J2HYV7#2}\\
\includegraphics[width=\pwidth]{#1SW58_ASW0007iwp_4XBJWT3COV#2}%
\includegraphics[width=\pwidth]{#1SW02_ASW000619d_011489#2}%
\includegraphics[width=\pwidth]{#1SW19_ASW0001ld7_OS3CYAKLRT#2}\\
\includegraphics[width=\pwidth]{#1SW09_ASW0002asp_5EKMWWVJHL#2}%
%\includegraphics[width=\pwidth]{#1SW36_ASW000096t_7IPP7LWVOF#2}\\
\includegraphics[width=\pwidth]{#1SW29_ASW0008qsm_TOFS7JNGEK#2}%
\includegraphics[width=\pwidth]{#1SW57_ASW0008pag_5SXGXQYY6V#2}\\
}

@@

\begin{table*}
  \caption{Categorisation of SW models}
  \label{tab:models}
  \include{table}
\end{table*}

@@

% The best way to enter references is to use BibTeX:
\bibliographystyle{mnras}
\bibliography{bib/bibli} % if your bibtex file is called example.bib

@@

\section{TODO}
\listoftodos

>>>>

\def\includeten#1#2{
\includegraphics[width=\pwidth]{#1ASW0007iwp_4XBJWT3COV#2}%
\includegraphics[width=\pwidth]{#1ASW0007xrs_JHC3J2HYV7#2}%
\includegraphics[width=\pwidth]{#1ASW0008pag_5SXGXQYY6V#2}\\
\includegraphics[width=\pwidth]{#1ASW0007k4r_N7LTELSYTM#2}%
\includegraphics[width=\pwidth]{#1ASW00096rm_4Q3YCEWGLN#2}%
\includegraphics[width=\pwidth]{#1ASW0001ld7_OS3CYAKLRT#2}\\
\includegraphics[width=\pwidth]{#1ASW0002asp_5EKMWWVJHL#2}%
\includegraphics[width=\pwidth]{#1ASW0008qsm_TOFS7JNGEK#2}%
\includegraphics[width=\pwidth]{#1ASW000619d_011489#2}\\
%\includegraphics[width=\pwidth]{#1ASW000096t_7IPP7LWVOF#2}%
}

\def\includezehn#1#2{
\includegraphics[width=\pwidth]{#1SW58_ASW0007iwp_4XBJWT3COV#2}%   L
\includegraphics[width=\pwidth]{#1SW28_ASW0007xrs_JHC3J2HYV7#2}%   L
\includegraphics[width=\pwidth]{#1SW57_ASW0008pag_5SXGXQYY6V#2}\\% X
\includegraphics[width=\pwidth]{#1SW05_ASW0007k4r_N7LTELSYTM#2}%   I
\includegraphics[width=\pwidth]{#1SW42_ASW00096rm_4Q3YCEWGLN#2}%   I
\includegraphics[width=\pwidth]{#1SW19_ASW0001ld7_OS3CYAKLRT#2}\\% I
\includegraphics[width=\pwidth]{#1SW09_ASW0002asp_5EKMWWVJHL#2}%   S
\includegraphics[width=\pwidth]{#1SW29_ASW0008qsm_TOFS7JNGEK#2}%   S
\includegraphics[width=\pwidth]{#1SW02_ASW000619d_011489#2}\\%     S
%\includegraphics[width=\pwidth]{#1SW36_ASW000096t_7IPP7LWVOF#2}%
}

@@

\input parts/summary

@@

\bibliographystyle{mnras}
\bibliography{bib/bibli}

@@

% \section{TODO}
% \listoftodos

### 2016-11-23 parts/intro.tex
figure changes

@@

In Section~\ref{sec:summary} and Table~\ref{tab:models} we display a
concise characterisation of each modelled system, according to the
image morphology and how clear or indistinct it is, whether the mass
map and synthetic lensed image appear to be plausible, and how the
model mass compares with the estimated stellar and full-halo masses.

Table~\ref{tab:models} shows a summary of the analysis for many candidates.
Missing rows are due to photometry data not available.

\begin{itemize}
\item Morphology from Figure~\ref{fig:markedup}.
\begin{itemize}
\item The image morphology concisely described: D for double, and
  quads in sub-categorised in four ways
  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
  SW28), SQ for short-axis quads (as in Figure~SW02,
  SW09, SW29, SW42), IQ for inclined quads
  (as in Figure~SW05) and CQ for very symmetric core quads.
\item Whether the images are unblended.  Distinct unblended images (as
  in Figures~SW05 and SW42) are an advantage in
  modelling, but not essential.
\item Whether all images are discernable.  The topography of an
  arrival-time surface, as encoded by a spaghetti diagram, may require
  more images than are visible.  For example, in Figure~SW58,
  the modeller has put in a conjectural saddle point near the lensing
  galaxy.
\item Whether the lens is fairly isolated.
\end{itemize}
\item Mass model
\begin{itemize}
\item Whether the arrival-time surface and synthetic image are
  plausible.  For SW36 the model implies extra images or a long arc,
  which are not seen.  Figures~\ref{fig:arriv} and \ref{fig:synth}.
\item Whether the mass map is reasonable. Figure~\ref{fig:kappa}.
\end{itemize}
\item Stellar mass. Figure~\ref{fig:stelmass}.
\end{itemize}

>>>>

\begin{itemize}
\item Morphology from Figure~\ref{fig:markedup}.
\begin{itemize}
\item The image morphology concisely described: D for double, and
  quads in sub-categorised in four ways
  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
  SW28), SQ for short-axis quads (as in Figure~SW02,
  SW09, SW29, SW42), IQ for inclined quads
  (as in Figure~SW05) and CQ for very symmetric core quads.
\item Whether the images are unblended.  Distinct unblended images (as
  in Figures~SW05 and SW42) are an advantage in
  modelling, but not essential.
\item Whether all images are discernable.  The topography of an
  arrival-time surface, as encoded by a spaghetti diagram, may require
  more images than are visible.  For example, in Figure~SW58,
  the modeller has put in a conjectural saddle point near the lensing
  galaxy.
\item Whether the lens is fairly isolated.
\end{itemize}
\item Mass model
\begin{itemize}
\item Whether the mass map is reasonable. Figure~\ref{fig:kappa}.
\item Whether the arrival-time surface and synthetic image are
  plausible.  For SW36 the model implies extra images or a long arc,
  which are not seen.  Figures~\ref{fig:arriv} and \ref{fig:synth}.
\end{itemize}
\item Stellar mass. Figure~\ref{fig:stelmass}.
\end{itemize}

@@
